\section{Mechanics}
\def\ee{\vc\varepsilon}
\newcommand{\eq}[1]{\begin{equation}#1\end{equation}}
\def\nn{\vc n}
% \def{\tr}{\operatorname{tr}}
\def\uu{\vc u}

Deformation of the porous media is modelled by the stationary linear elasticity equation:
\eq{\label{eq:lin_el} -\div(\delta\tn \sigma(\uu)) = \delta\vc f + \vc f_C + \vc f_H. }
Here $\uu$ \units{}{1}{} is the unknown displacement vector field with 3 components. The stress tensor is given by the Hooke law
\eq{ \tn\sigma(\uu) - \tn\sigma_0 = \tn C\widetilde\ee(\uu) = 2\mu\widetilde\ee(\uu) + \lambda(\tn I:\widetilde\ee(\uu))\tn I }
in terms of the \hyperA{Mechanics-LinearElasticity-FE-Data::initial-stress}{initial stress} $\tn\sigma_0$ [$\mathrm{Pa}$], and the Lam\'e parameters
\eq{ \mu = \frac{E}{2(1+\nu)},\quad \lambda = \frac{E\nu}{(1+\nu)(1-2\nu)}, }
where $E$ [$\mathrm{Pa}$] is the \hyperA{Mechanics-LinearElasticity-FE-Data::young-modulus}{Young modulus} and  $\nu$ \units{}{}{} is the \hyperA{Mechanics-LinearElasticity-FE-Data::poisson-ratio}{Poisson's ratio}.
The strain tensor in $\Omega_d$ is defined as follows:
\eq{ \widetilde\ee_d(\uu) = \frac12(\nabla\uu_d+\nabla\uu_d^\top) + \begin{cases}0&\mbox{ if }d=3,\\\frac1{\delta_d}\sum_{i=1}^n\delta_{d+1}^i\uu_{d+1}^i\otimes_s\nn_{d+1}^i & \mbox{ else}.\end{cases} }
Here $\vc a\otimes_s\vc b:=\frac12(\vc a\otimes\vc b+\vc b\otimes\vc a)$.

The symbol $\vc f$ stands for the \hyperA{Mechanics-LinearElasticity-FE-Data::load}{body load} [$\mathrm{Nm}^{-3}$].


\paragraph{Hydromechanical coupling.}
The mechanics equation \eqref{eq:lin_el} is coupled to flow by the term
\eq{ \vc f_H = -\nabla(\delta\alpha \varrho_l g(h-h^0)), }
where $h$, $h^0$ [$\mathrm{m}$] is the pressure head and its initial value, respectively, $\alpha$ \units{}{}{} is the \hyperA{Coupling-Iterative-Data::biot-alpha}{Biot coefficient}, $\varrho_l$ \units{1}{-3}{} is the \hyperA{Coupling-Iterative-Data::fluid-density}{fluid density} and $g$ \units{}{1}{-2} is the \hyperA{Coupling-Iterative-Data::gravity}{gravitational acceleration}.
Conversely, the deformation affects the flow via the additional term
\eq{\label{eq:fluid_source_div_u} F_M = -\partial_t(\delta\alpha\widetilde\div\uu) }
on the right hand side of \eqref{eq:continuity}, where $\widetilde\div\uu:=\tn I:\widetilde\ee(\uu)$.
Adding the coupling terms $\vc f_H$, $F_M$ into the equation of mechanics \eqref{eq:lin_el} and flow \eqref{eq:continuity}, respectively, leads to the Biot-type poroelasticity system:
\eq{ -\div(\delta\widehat\sigma(\uu,h)) = \delta\vc f + \vc f_C, }
\eq{ \partial_t(\delta(Sh + \alpha\widetilde\div\uu)) + \div\vc q = F. }
Here
\eq{ \widehat\sigma(\uu,h):=\sigma(\uu)-\alpha\varrho_l g(h-h^0)\tn I }
is the total poroelastic stress, while $\sigma(\uu)$ plays the role of the effective (mechanical) stress.

The numerical solution of coupled hydro-mechanical problems is solved by an iterative splitting, where, in order to achieve convergence, the flow equation is modified as follows:
\eq{ \partial_t(\delta(S+S_{extra})h) + \div\vc q = F + F_M + \partial_t(\delta S_{extra} h_{old}). }
Here $h_{old}$ is the previous value of pressure head in the iteration process and
\eq{ S_{extra}=\iota\frac{\alpha^2}{2\varrho_l g(\tfrac23\mu+\lambda)} }
 is an extra storativity coefficient whose value affects the rate of convergence.
It can be manually tuned using the \hyperA{Coupling-Iterative::iteration-parameter}{iteration parameter} $\iota$.


\paragraph{Boundary conditions.}
Given the decomposition $\partial\Omega_d=\Gamma_D\cup\Gamma_{DN}\cup\Gamma_T\cup\Gamma_S$ and denoting by $\nn$ the unit outward normal vector, we impose the following \hyperA{Mechanics-LinearElasticity-FE-Data::bc-type}{boundary conditions}:
\begin{itemize}
\item \textbf{displacement} condition prescribes
\eq{ \uu = \uu_D \mbox{ on }\Gamma_D }
via \hyperA{Mechanics-LinearElasticity-FE-Data::bc-displacement}{given displacement} $\uu_D$ \units{}{1}{}.
\item \textbf{displacement\_n}: Displacement is prescribed only in the normal component, in tangent directions(s) zero traction is assumed:
\eq{ \left.\begin{aligned}\uu\cdot\nn &= \uu_D\cdot\nn\\
(\widehat\sigma(\uu,h)\nn)_\tau &= \vc 0\end{aligned}\right\} \mbox{ on }\Gamma_{DN}. }
Here $\vc a_\tau := \vc a - (\vc a\cdot\nn)\nn$ is the projection of a vector $\vc a$ to the tangent plane of the boundary.
\item \textbf{traction} condition (default) is imposed via \hyperA{Mechanics-LinearElasticity-FE-Data::bc-traction}{given traction} $\vc t_N$ [$\mathrm{Pa}$]:
\eq{ \widehat\sigma(\uu,h)\nn = \vc t_N \mbox{ on }\Gamma_T. }
\item \textbf{stress} condition is the same type as \textbf{traction}, but instead of traction the user supplies the full \hyperA{Mechanics-LinearElasticity-FE-Data::bc-stress}{stress tensor} $\tn\sigma_N$ [$\mathrm{Pa}$]:
\eq{ \widehat\sigma(\uu,h)\nn = \tn\sigma_N\nn \mbox{ on }\Gamma_S. }
\end{itemize}


\paragraph{Communication between dimensions.}
The mechanical interaction on the interface between $\Omega_{d+1}$ and $\Omega_d$ is realized via the traction condition on the boundary of $\Omega_{d+1}$:
\eq{ \widehat\sigma(\uu^i_{d+1},h^i_{d+1})\nn^i_{d+1} = \vc t^i_{d+1,d}, }
where
\eq{ \vc t^i_{d+1,d} = \sigma^U_{d+1,d}\left(\sigma_0+\frac{2\delta_{d+1}^i}{\delta_d}\tn C_d\left((\uu_{d+1}^i-\uu_d)\otimes\nn_{d+1}^i\right)-\alpha_d \varrho_l g(h_d-d^0_d)\tn I\right)\nn_{d+1}^i }
and $\sigma^U_{d+1,d}$ \units{}{}{} is the \hyperA{Mechanics-LinearElasticity-FE-Data::fracture-sigma}{transition coefficient}.
The force term in $\Omega_d$ due to the interaction with $\Omega_{d+1}$ is
\eq{ \vc f_{Cd} = \begin{cases}\vc 0 & \mbox{ if }d=3,\\\sum_{i=1}^n\delta_{d+1}^i\vc t^i_{d+1,d} & \mbox{ else}.\end{cases} }

\paragraph{Fracture contact mechanics.}
The linear elastic model does not prevent the self-penetration of the deformed porous material.
To avoid this unphysical behaviour, the user has to switch on the \hyperA{Mechanics-LinearElasticity-FE::contact}{contact} parameter.
Then the following contact condition is applied to all fracture elements:
\eq{ \tilde\delta_d(\uu) := \delta_d-\sum_{i=1}^n\delta_{d+1}^i\uu_{d+1}^i\cdot\nn_{d+1}^i \ge \delta_d^{min}, }
where $\tilde\delta_d(\uu)$ \units{}{3-d}{} is the cross-section of the deformed fracture, $\delta_d^{min}$ \units{}{3-d}{} is the \hyperA{Mechanics-LinearElasticity-FE-Data::cross-section-min}{minimal cross-section} of the fracture.
In the case $d=2$, the minimal cross-section is just the contact distance.
For $1d$ fractures/channels, $\delta^{min}$ corresponds to the minimal contact area.
When contact conditions are active, the mechanical model is solved as a quadratic programming problem with linear constraints.

\paragraph{Output fields.}
The mechanics equation provides several fields for output:
\begin{itemize}
    \item \hyperA{Mechanics-LinearElasticity-FE-OutputFields::displacement}{displacement}: The computed displacement vector field $\uu$;
    \item \hyperA{Mechanics-LinearElasticity-FE-OutputFields::effective-stress}{effective\_stress}: The effective (mechanical) stress tensor $\sigma(\uu)$;
    \item \hyperA{Mechanics-LinearElasticity-FE-OutputFields::total-stress}{total\_stress}: The total (poroelastic) stress tensor $\widehat\sigma(\uu,h)$;
    \item \hyperA{Mechanics-LinearElasticity-FE-OutputFields::mean-effective-stress}{mean\_effective\_stress}: The mean of the principal effective stresses, i.e. $\sigma_m:=\frac13\tn I:\tn\sigma(\uu)$;
    \item \hyperA{Mechanics-LinearElasticity-FE-OutputFields::mean-total-stress}{mean\_total\_stress}: The mean of the principal total stresses, i.e. $\widehat\sigma_m:=\frac13\tn I:\widehat\sigma(\uu,h)$;
    \item \hyperA{Mechanics-LinearElasticity-FE-OutputFields::von-mises-stress}{von\_mises\_stress}: $\sigma_{VM}:=\sqrt{\frac32\tn\sigma_d:\tn\sigma_d}$, where $\tn\sigma_d:=\tn\sigma(\uu)-\sigma_m\tn I$ is the deviatoric stress.
    Equivalently, von Mises stress can be expressed as
    \[ \sigma_{VM} = \sqrt{\frac12\left((\sigma_1-\sigma_2)^2+(\sigma_1-\sigma_3)^2+(\sigma_2-\sigma_3)^2\right)}, \]
    where $\sigma_{1,2,3}$ are the principal stresses, i.e. eigenvalues of $\tn\sigma(\uu)$ (or equivalently $\widehat\sigma(\uu,h)$);
    \item \hyperA{Mechanics-LinearElasticity-FE-OutputFields::cross-section-updated}{cross\_section\_updated}: The cross-section $\tilde\delta_d(\uu)$ after deformation;
    \item \hyperA{Mechanics-LinearElasticity-FE-OutputFields::displacement-divergence}{displacement\_divergence}: $\widetilde\div\uu_d$.
\end{itemize}


\paragraph{Stress tensors and sign convention.}
We use the engineering convention, according to which, tensile stress is positive.
This applies to the values of $\sigma(\uu)$, $\widehat\sigma(\uu,h)$, $\sigma_0$ and $\sigma_N$.
It means that, for example, the initial stress $\sigma_0$ in a rock massive will typically have negative principal values.
Accordingly, an outward orientation of the traction $\vc t_N$ indicates tension and vice versa.

We also emphasize that the initial stress is not an initial value in the mathematical sense, but rather a pre-existing stress that is always present even if no other forces are applied.