% ***************************************** SYMBOLS
\def\abs#1{\lvert#1\rvert}
\def\argdot{{\hspace{0.18em}\cdot\hspace{0.18em}}}
\def\avg#1{\left\{#1\right\}_\omega}
\def\D{{\tn D}}
\def\div{\operatorname{div}}
\def\Eh{\mathcal E_h}       % edges of \Th
\def\Ehcom{\mathcal E_{h,C}}         % edges of \Th on interface with lower dimension
\def\Ehdir{\mathcal E_{h,D}}         % Dirichlet edges of \Th
\def\Ehint{\mathcal E_{h,I}}       % interior edges of \Th
\def\grad{\nabla}
\def\jmp#1{[#1]}
\def\n{\vc n}
\def\vc#1{\mathbf{\boldsymbol{#1}}}     % vector
\def\R{\mathbb R}
\def\sc#1#2{\left(#1,#2\right)}
\def\Th{\mathcal T_h}       % triangulation
\def\th{\vartheta}
\def\tn#1{{\mathbb{#1}}}    % tensor
\def\Tr{\operatorname{Tr}}
\def\where{\,|\,}
%***************************************************************************


\section{Transport of substances}

The motion of substances dissolved in water is governed by the \emph{advection}, and the \emph{hydrodynamic dispersion}.
In $\Omega_d$, $d\in\{1,2,3\}$, we consider the following system of mass balance equations:
\begin{equation}
    \label{e:ADE}
   \partial_t ( \delta \th c^i) + \div ( \vc q c^i ) - \div (\th \delta \D^i \grad c^i ) = F_S^i + F_C(c^i) + F_R(c^1,\dots, c^s).
\end{equation}
For $d\in\{1,2\}$ this form can be derived as in Section \ref{sc:ad_on_fractures} using $w:=\delta\th c^i$, $u:=c^i$, $\tn A:=\delta\th\tn D^i$, $\vc b:=\vc v=\frac{\vc q}{\th\delta}$.
The principal unknown is the concentration $c^i$ \units{1}{-3}{} of a substance $i\in\{1,\dots, s\}$, which means weight of the substance in unit volume of the water.
Other quantities are:
\begin{itemize}

\item $\th$ \units{}{}{} is the \hyperA{TransportDG-BulkData::por-m}{porosity}, i.e. fraction of space occupied by water and the total volume.
\item The hydrodynamic dispersivity tensor $\D^i$ \units{}{2}{-1} has the form
\begin{equation} 
  \label{eqn:transport_disp}
  \D^i =D_m^i \tau \tn I + \abs{\vc v}\left(\alpha_T^i \tn I + (\alpha_L^i - \alpha_T^i) \frac{\vc v \otimes \vc v}{\abs{\vc v}^2}\right),
\end{equation}
which represents (isotropic) molecular diffusion, and mechanical dispersion in longitudal and transversal direction to the flow.
Here $D_m^i$ \units{}{2}{-1} is the \hyperA{TransportDG-BulkData::diff-m}{molecular diffusion coefficient} of the $i$-th substance (usual magnitude in clear water is $10^{-9}$), $\tau=\th^{1/3}$ is the tortuosity (by \cite{millington_quirk}), $\alpha_L^i$ \units{}{1}{} and $\alpha_T^i$ \units{}{1}{} is the \hyperA{TransportDG-BulkData::disp-l}{longitudal dispersivity} and the \hyperA{TransportDG-BulkData::disp-t}{transversal dispersivity}, respectively.
Finally, $\vc v$ \units{}{1}{-1} is the \emph{microscopic} water velocity, related to the Darcy flux $\vc q$ by the relation $\vc q = \th\delta\vc v$.
The value of $D_m^i$ for specific substances can be found in literature (see e.g. \cite{cislerova_vogel}).
For instructions on how to determine $\alpha_L^i$, $\alpha_T^i$ we refer to \cite{marsily,domenico_schwartz}.

\item $F_S^i$ \units{1}{-d}{-1} represents the density of concentration sources.
Its form is:
\begin{equation}
 F_S^i = \varrho^i_S + (c_S^i-c^i)\sigma_S. \label{eqn:transport_sources}
\end{equation}
Here $\varrho_S^i$ \units{1}{-d}{-1} is the \hyperA{TransportDG-BulkData::sources-density}{density of concentration sources}, $c_S^i$ is an \hyperA{TransportDG-BulkData::sources-conc}{equilibrium concentration} and $\sigma_S^i$ is the \hyperA{TransportDG-BulkData::sources-sigma}{concentration flux}.

\item $F_C(c^i)$ \units{1}{-d}{-1} is the density of concentration sources due to exchange between regions with different dimensions, see \eqref{e:FC} below.

\item The reaction term $F_R(\dots)$ \units{1}{-d}{-1} is currently neglected.
\end{itemize}



\paragraph{Initial and boundary conditions.}
At time $t=0$ the concentration is determined by the \hyperA{TransportDG-BulkData::init-conc}{initial condition}
$$ c^i(0,\vc x) = c^i_0(\vc x). $$
The physical boundary $\partial\Omega_d$ is decomposed into the parts $\Gamma_I\cup\Gamma_D\cup\Gamma_N\cup\Gamma_R$, which may change during simulation time.
The first part $\Gamma_I$ is further divided into two segments:
\begin{align*}
\Gamma_I^+(t) &= \{\vc x\in \partial\Omega_d\where \vc q(t,\vc x)\cdot\vc n(\vc x)<0\},\\
\Gamma_I^-(t) &= \{\vc x\in \partial\Omega_d\where \vc q(t,\vc x)\cdot\vc n(\vc x)\ge 0\},
\end{align*}
where $\vc n$ stands for the unit outward normal vector to $\partial\Omega_d$.
We prescribe the following boundary conditions:
On the inflow parts $\Gamma_I^+\cup\Gamma_D$, the user must provide \hyperA{TransportDG-BoundaryData::bc-conc}{Dirichlet boundary condition} $c_D^i$ for concentrations:
$$ c^i = c^i_D \mbox{ on }\Gamma_I^+\cup\Gamma_D. $$
On $\Gamma_I^-$ we impose homogeneous Neumann boundary condition:
$$ -\th\delta\D^i\nabla c^i\cdot\vc n = 0 \mbox{ on }\Gamma_I^-, $$
on $\Gamma_N$ we impose Neumann boundary condition with user-defined \hyperA{TransportDG-BoundaryData::bc-flux}{concentration flux} $f^i_N$:
$$ -\th\delta\D^i\nabla c^i\cdot\vc n = f^i_N \mbox{ on }\Gamma_N, $$
and finally on $\Gamma_R$ we impose Robin boundary condition through \hyperA{TransportDG-BoundaryData::bc-robin-sigma}{transition parameter} $\sigma^i_R$ and \hyperA{TransportDG-BoundaryData::bc-conc}{reference concentration} $c^i_D$:
$$ -\th\delta\D^i\nabla c^i\cdot\vc n = \sigma^i_R(c^i-c^i_D) \mbox{ on }\Gamma_R. $$






\paragraph{Communication between dimensions.}
Transport of substances is considered also on interfaces of physical domains with adjacent dimensions (i.e. 3D-2D and 2D-1D, but not 3D-1D).
Denoting $c_{d+1}$, $c_d$ the concentration of a given substance in $\Omega_{d+1}$ and $\Omega_d$, respectively, the comunication on the interface between $\Omega_{d+1}$ and $\Omega_d$ is described by the quantity
\begin{equation}
  \label{e:inter_dim_flux}
  q^c_{d+1,d} = \sigma^c_{d+1,d} \frac{\delta_{d+1}^2}{\delta_d}2\th_d\D_d:\n\otimes\n ( c_{d+1} - c_d) + \begin{cases}q^w_{d+1,d} c_{d+1} & \mbox{ if }q^w_{d+1,d}\ge 0,\\q^w_{d+1,d} \frac{\th_d}{\th_{d+1}} c_d & \mbox{ if }q^w_{d+1,d}<0,\end{cases}
\end{equation}
where
\begin{itemize}
\item $q^c_{d+1,d}$ \units{1}{-d}{-1} is the density of concentration flux from $\Omega_{d+1}$ to $\Omega_d$,
\item $\sigma^c_{d+1,d}$ \units{}{}{} is a \hyperA{TransportDG-BulkData::sigma-c}{transition parameter}.
Its value determines the mass exchange between dimensions whenever the concentrations differ.
In general, it is recommended to leave the default value $\sigma^c=1$ or to set $\sigma^c=0$ (when exchange is due to water flux only).
\item $q^w_{d+1,d}$ \units{}{3-d}{-1} is the water flux from $\Omega_{d+1}$ to $\Omega_d$, i.e. $q^w_{d+1,d} = \vc q_{d+1}\cdot\n_{d+1}$.
\end{itemize}
The communication between dimensions is incorporated as the total flux boundary condition for the problem on $\Omega_{d+1}$:
\begin{equation}
\label{e:FC}
-\th\delta\D\nabla c\cdot\vc n + q^w c = q^c
\end{equation}
and a source term in $\Omega_d$:
\begin{equation}
F_C^3 = 0,\quad
F_C^2 = q^c_{32},\quad
F_C^1 = \frac{\delta_2}{\delta_1}q^c_{32} + q^c_{21}.
\end{equation}


\paragraph{Dual porosity.}
Up to now we have described the transport equation for the single porosity model. The dual porosity model splits the mass into to zones the mobile zone and the immbile zone. 
Both occupy the same macroscopic volume, however on the microscopic scale, the immobile zone is formed by the dead-end pores, where the liquid is traped and can not pass through.
The rest of the pore volume is ocuppied by the mobile zone. Since the liquid in the immobile pores is immobile, the exchange of the substance is only due to molecular diffusion.
We consider simple nonequilibrium linear model:
\begin{align}
    \theta_m \partial_t c_m &= \alpha ( c_i - c_m), \\
    \theta_i \partial_t c_i &= \alpha ( c_m - c_i) 
\end{align}
where $c_m$ is the concentration in the mobile zone, $c_i$ is the concentration in the immobile zone, $\alpha$ is a diffusion parameter, $\theta_m$ and $\theta_i$ are porosities of the mobile zone and the immobile zone respectively, while 
\[
  \theta_m +\theta_i =\theta.
\]

The solution of this system is:
\begin{align}
     c_m(t) &= (c_m(0) - c_a(0)) \exp(- \alpha(\frac{1}{\theta_m} + \frac{1}{\theta_i}) t) + c_a(0), \\
     c_i(t) &= (c_i(0) - c_a(0)) \exp(- \alpha(\frac{1}{\theta_m} + \frac{1}{\theta_i}) t) + c_a(0)
\end{align}
where $c_a$ is weighted average:
\[
  c_a = \frac{\theta_m c_m + \theta_i c_i}{\theta_m + \theta_i}.
\]


\paragraph{Mass balance.}
The advection-dispersion equation satisfies the balance of mass in the following form:
$$ m^i(0) + \int_0^t s^i(\tau) \,d\tau - \int_0^t f^i(\tau) \,d\tau = m^i(t) $$
for any instant $t$ in the computational time interval and any substance $i$.
Here
$$ m^i(t) := \sum_{d=1}^3\int_{\Omega^d}\delta_d\th c^i(t,\vc x)\,d\vc x, $$
$$ s^i(t) := \sum_{d=1}^3\int_{\Omega^d}F_S(t,\vc x)\,d\vc x, $$
$$ f^i(t) := \sum_{d=1}^3\int_{\partial\Omega^d}\left(\th\delta_d c^i(t,\vc x)\vc q(t,\vc x) - \th\delta_d\D^i\nabla c^i(t,\vc x)\right)\cdot\vc n \,d\vc x $$
is the mass \units{1}{}{}, the volume source \units{1}{}{-1} and the mass flux \units{1}{}{-1} of $i$-th substance at time $t$, respectively.
The mass, flux and source on every geometrical region is calculated at each computational time step and the values together with the control sums are written to the file \texttt{mass\_balance.txt}.





